conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-06-20 paper/paper.Rmd
Updated paper intro

These social contact surveys exist for a few countries. As an example, @mossong2008 the "POLYMOD" study covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008]. However, what do we do when we want to (?)look at/estimate contact rates in different countries that have not been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A very popular approach by Prem et al projected from the POLYMOD study to 152 countries [@prem2017]. This which was later updated to include contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country. One limitation of this is that the predictions were not provided at smaller grained regons. This might be important, if for example, a public health group needed to make predictions for specific areas. It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse.

>>>>

These social contact surveys exist for a few countries. As an example, the "POLYMOD" study by @mossong2008 covered 8 European countries: Belgium, Germany, Finland, Great Britain, Italy, Luxembourg, The Netherlands, and Poland [@mossong2008]. However, what do we do when we want to (?)look at/estimate contact rates in other countries that have not been measured? We can use this existing data to help us project to countries or places that do not have empirical survey data. These are called "synthetic contact matrices". A popular approach by @prem2017 projected from the POLYMOD study to 152 countries. This was later updated to include synthetic contact matrices for 177 countries at "urban" and "rural" levels for each country [@prem2021].

However not all countries were included in this list from @prem2021, and for some analyses these synthetic contact matrices were at a large area, such as "urban" or "rural" for a given country. One limitation of this is that the predictions were not provided at smaller grained regions. This might be important, if for example, a public health group needed to make predictions for specific areas. It was challenging to apply the methodology used by Prem et al, as while their analysis code was provided, it was not designed for reuse.
